\malg: a novell interest management algorithm for distributed simulations of MMGs

### 2008-05-01 trunk/textos/dsrt/engaoi.tex
eng

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A novell interest management algorithm for distributed simulations of MMGs}

@@

Before sending the state of an entity to a client, the last transmission time is checked. The next transmission is then scheduled to occur after a certain interval. If the relevance of that state is 1, the normal update interval will be used. If it is less than 1, the normal interval is divided by the relevance. For example, let the normal update interval of a game be 200 ms. If the avatar $A_i$, which just sent a state update packet to $A_j$, is at a distance from $A_i$ such that its relevance is 0.5, the next transmission will only happen after an interval of 200 divided by 0.5. So, the player controlling $A_j$ will only receive an update of $A_i$ after 400 ms. Despite this interval is still less than a half second, it represents a reduction of the state update frequecy of $A_i$ in 50\%. As they are at a greater distance from one another, and the interval was increased only by 200 ms, this variation will probably be imperceptible by the player who controls $A_j$.

@@

\begin{itemize}
 \item Normal update interval: 250 ms;
 \item State update packet size for one entity: 100 bytes;
 \item Duration of each simulated game session: 20 min;
 \item Virtual environment area: 750 x 750;
 \item View distance: 120;
 \item Critical distance: 40;
 \item View angle: 180°.
\end{itemize}

Several simulations were executed, in order to compare the described interest management algorithms. The number of avatars in the environment was one of the variables analyzed, to verify the scalability. The algorithms compared were the ones with circle, circle with attenuation and field of view based area of interest and the proposed algorithm, \malg. To demonstrate how much traffic reduction each one of these achieve, simulations in which no type of interest management was used - and the server sent to the client state updates of all entities in the environment - were also performed.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\malg: a novell interest management algorithm for distributed simulations of MMGs}

@@

Before sending the state of an entity to a client, the last transmission time is checked. The next transmission is then scheduled to occur after a certain interval. If the relevance of that state is 1, the normal update interval will be used. If it is less than 1, the normal interval is divided by the relevance. For example, let the normal update interval of a game be \mbox{200 ms}. If the avatar $A_i$, which just sent a state update packet to $A_j$, is at a distance from $A_i$ such that its relevance is 0.5, the next transmission will only happen after an interval of 200 divided by 0.5. So, the player controlling $A_j$ will only receive an update of $A_i$ after 400 ms. Despite this interval is still less than a half second, it represents a reduction of the state update frequecy of $A_i$ in 50\%. As they are at a greater distance from one another, and the interval was increased only by 200 ms, this variation will probably be imperceptible by the player who controls $A_j$.

@@

\begin{itemize}
 \item Normal update interval: 250 ms;
 \item State update for one entity: 100 bytes UDP packet;
 \item Duration of each simulated game session: 20 min;
 \item Virtual environment area: 750 x 750;
 \item View distance: 120;
 \item Critical distance: 40;
 \item View angle: 180°.
\end{itemize}

Several simulations were executed, in order to compare the described interest management algorithms. The number of avatars in the environment was varied in order to measure the scalability. The algorithms compared were the ones with circle, circle with attenuation and field of view based area of interest and the proposed algorithm, \malg. To demonstrate how much traffic reduction each one of these achieve, simulations in which no type of interest management was used - and the server sent to the client state updates of all entities in the environment - were also performed.
